Instructions for \confname{} Proceedings

### 2019-05-13 papers/EMNLP2019/analysis2.tex

@@

\begin{table*}

%\begin{tabular}{lll}
%\toprule
%       relation &  types & tokens \\
%\midrule
%synonymy &  0.01 &  0.09 \\
%co-hyponymy &  0.03 &  0.07 \\
%hypernymy &  0.06 &  0.35 \\
%not-covered &  0.19 &  0.04 \\
%crossclassified &  0.70 &  0.47 \\
%\bottomrule
%\end{tabular}
% \small
% \begin{tabular}{llll}
% \toprule
%         relation & \% types & \% tokens & av. depth \\
% \midrule
%  co-hyponymy (closure, max depth=10) &  0.889 &  0.551 &       3.479 \\
%     hyponymy (closure, max depth=10) &  0.097 &  0.328 &       2.204 \\
%         synonymy &  0.015 &  0.121 &       1.000 \\
% \bottomrule
% \end{tabular}

\begin{tabular}{l|ll|ll|ll|ll|ll}
\toprule
      & \multicolumn{2}{c}{crossclassified} & \multicolumn{2}{c}{co-hyponymy} & \multicolumn{2}{c}{hypernymy} & \multicolumn{2}{c}{not-covered} & \multicolumn{2}{c}{synonymy} \\
         domain & typ & tok & typ & tok & typ & tok & typ &  tok & typ & tok \\
\midrule
 people &  0.725 &  0.618 &  0.019 &  0.032 &  0.051 &  0.293 &  0.200 &  0.038 &  0.005 &  0.019 \\
 clothing &  0.709 &  0.661 &  0.020 &  0.046 &  0.045 &  0.195 &  0.219 &  0.085 &  0.008 &  0.012 \\
 animals\_plants &  0.679 &  0.461 &  0.032 &  0.102 &  0.111 &  0.365 &  0.167 &  0.058 &  0.011 &  0.014 \\
 food &  0.590 &  0.433 &  0.031 &  0.033 &  0.104 &  0.432 &  0.267 &  0.089 &  0.009 &  0.013 \\
 vehicles &  0.635 &  0.329 &  0.026 &  0.083 &  0.059 &  0.239 &  0.271 &  0.089 &  0.008 &  0.260 \\
 home &  0.672 &  0.644 &  0.026 &  0.072 &  0.040 &  0.130 &  0.254 &  0.097 &  0.009 &  0.057 \\
 buildings &  0.780 &  0.725 &  0.026 &  0.038 &  0.045 &  0.156 &  0.138 &  0.058 &  0.011 &  0.022 \\
 \hline
 all &  0.731 &  0.574 &  0.033 &  0.057 &  0.076 &  0.256 &  0.147 &  0.050 &  0.013 &  0.064 \\
\bottomrule
\end{tabular}

\caption{Lexical relations between naming variants according to WordNet, for the set of name pairs where both words can be found in WordNet and stand in a \sz{should we produce this table for the different domains?} \gbt{yes, please. Maybe do rows domains, columns lexical relations (synymymy, hyponymy, co-hyponymy, other, not in wordnet), with subcolumns for types and tokens? And do percentages over rows -- for each domain, how many of the variants we find fall into each of the classes. This way we'll be able to see differences across domains.}}
\label{tab:rel}
\end{table*}

>>>>

Previous work on large-scale collections of labels or names of objects has (explicitly or implicitly) assumed that once naming data is canonical, linguistic alternatives of the canonical name can simply be retrieved from existing taxonomies like e.g.\ WordNet. 
If this was indeed the case, it would be feasible (and probably even desirable) to canonicalize object names during dataset collection, without loosing too much information about linguistic variations in natural object naming scenarios (like e.g.\ referring expression generation).
Hence, in this Section, we investigate to what extent the variation in object naming that we find in our MN data set (see previous Section) is covered by WordNet.

@@

\begin{table}
\small
\begin{tabular}{lcc|cc}
\toprule
 & \multicolumn{2}{c}{all MN variants} &  \multicolumn{2}{c}{MN $n > 10$} \\
        relation & \%token &    \%types & \%token &    \%types \\
\midrule
\multicolumn{2}{c}{\it easy to recover}\\
 meronymy &  0.3 &  0.9 &  0.8 &  1.0 \\
 synonymy &  1.8 &  6.4 &  2.5 &  7.2 \\
 hypernymy &  8.8 &  28.2 &  11.0 &  31.3 \\
\midrule
\multicolumn{2}{c}{\it difficult to recover}\\
holonymy.1 &  0.2 &  0.8 &  0.3 &  0.9 \\
 co-hyponymy &  4.8 &  6.2 &  6.0 &  6.4 \\
 hyponymy &  4.9 &  6.6 &  5.5 &  6.9 \\
 \midrule
 \multicolumn{2}{c}{\it not recoverable}\\
 name not covered &  7.8 &  2.8 &  5.8 &  2.1 \\
 rel not covered &  71.3 &  48.1 &  68.0 &  44.2 \\
\bottomrule

\end{tabular}
%\begin{tabular}{lll}
%\toprule
%       relation &  types & tokens \\
%\midrule
%synonymy &  0.01 &  0.09 \\
%co-hyponymy &  0.03 &  0.07 \\
%hypernymy &  0.06 &  0.35 \\
%not-covered &  0.19 &  0.04 \\
%crossclassified &  0.70 &  0.47 \\
%\bottomrule
%\end{tabular}
% \small
% \begin{tabular}{llll}
% \toprule
%         relation & \% types & \% tokens & av. depth \\
% \midrule
%  co-hyponymy (closure, max depth=10) &  0.889 &  0.551 &       3.479 \\
%     hyponymy (closure, max depth=10) &  0.097 &  0.328 &       2.204 \\
%         synonymy &  0.015 &  0.121 &       1.000 \\
% \bottomrule
% \end{tabular}

%\begin{tabular}{l|ll|ll|ll|ll|ll}
%\toprule
%      & \multicolumn{2}{c}{crossclassified} & \multicolumn{2}{c}{co-hyponymy} & \multicolumn{2}{c}{hypernymy} & \multicolumn{2}{c}{not-covered} & \multicolumn{2}{c}{synonymy} \\
%         domain & typ & tok & typ & tok & typ & tok & typ &  tok & typ & tok \\
%\midrule
% people &  0.725 &  0.618 &  0.019 &  0.032 &  0.051 &  0.293 &  0.200 &  0.038 &  0.005 &  0.019 \\
% clothing &  0.709 &  0.661 &  0.020 &  0.046 &  0.045 &  0.195 &  0.219 &  0.085 &  0.008 &  0.012 \\
% animals\_plants &  0.679 &  0.461 &  0.032 &  0.102 &  0.111 &  0.365 &  0.167 &  0.058 &  0.011 &  0.014 \\
% food &  0.590 &  0.433 &  0.031 &  0.033 &  0.104 &  0.432 &  0.267 &  0.089 &  0.009 &  0.013 \\
% vehicles &  0.635 &  0.329 &  0.026 &  0.083 &  0.059 &  0.239 &  0.271 &  0.089 &  0.008 &  0.260 \\
% home &  0.672 &  0.644 &  0.026 &  0.072 &  0.040 &  0.130 &  0.254 &  0.097 &  0.009 &  0.057 \\
% buildings &  0.780 &  0.725 &  0.026 &  0.038 &  0.045 &  0.156 &  0.138 &  0.058 &  0.011 &  0.022 \\
% \hline
% all &  0.731 &  0.574 &  0.033 &  0.057 &  0.076 &  0.256 &  0.147 &  0.050 &  0.013 &  0.064 \\
%\bottomrule
%\end{tabular}

\caption{Lexical relations between naming variants in WN and the VG name according to WordNet}
\label{tab:rel}
\end{table}
